Disturbance-aware minimum-time planning strategies for motorsport vehicles with probabilistic safety certificates

### 2025-06-11 performance_comparison.tex
[MM] Some software detail added

@@

>>>>

The chosen sector has been discretized with 140 intervals, corresponding to one grid point each 0.43\,m. 
The optimization problems are formulate within the CasADi+MATLAB framework~\cite{Andersson:MPC:2019}, and solved using the interior point method implemented in IPOPT~\cite{Wachter:MP:2006}.

@@

% Calculus times 
We provide here some details on the software implementation and computation times to complement the comparison between the two proposed methods. All optimizations were performed on a machine equipped with an Intel Core i9-13980HX processor and 32\,Gb of RAM. Only the solver time is reported for each configuration, as the problem build time is negligible.
The nominal problem involves 4200 optimization variables and is solved in 7.5\,s. The open-loop configuration, using a prediction horizon of $H=4$ as adopted in this study, includes 48300 variables and requires 128\,s to solve. The closed-loop method first solves the nominal problem, then performs the Step~2 in 0.5\,s, and finally formulates an additional problem with 14700 variables, which is solved in 33\,s, resulting in a total computation time of 40\,s.
